The Influence of Radial Drift and Gas Accretion on the C/O Ratio in Protoplanetary Disks

### 2016-04-14 Dissertate-Harvard-LaTeX/chapters/chapter1.tex
upd

Many static studies reproduce a canonical $\MC \sim 10 M_\oplus$.  However, \citet[hereafter R06]{Raf11, rafikov06} finds a wide range of values, $0.1 M_\oplus \lesssim \MC \lesssim 100 M_\oplus$, depending on the planetesimal accretion rate and disk parameters. % \citep[see also][]{Raf11}.  
Section \ref{sec:placc} compares our results to R06.  A general limitation of static models is the neglect of heat generated by atmospheric collapse, which can transform the core accretion instability into a slower process of Kelvin-Helmholtz (KH) contraction.

@@

This paper is organized as follows. Section \S\ref{sec:model} describes our model of atmospheric growth.  In Section \S\ref{sec:coolingan}, we develop a simplified analytic version of our atmospheric model.  We describe the structure and evolution of our atmosphere solutions in Section \S\ref{sec:KH}.   Section \S\ref{sec:critical} gives our final results for growth timescales and critical core masses.  We discuss some neglected effects in Section \S\ref{sec:neglected} and summarize our findings in Section \S\ref{sec:conclusions}.  Some detailed derivations are presented in the appendices.

@@

To model the accretion of gas by a solid protoplanet, we develop a simplified two-layer model for time-dependent atmospheric growth via cooling, i.e. KH contraction.  With a convective interior and radiative exterior, this model is motivated by similar models of hot Jupiters \citep{ab06, ym10}.

@@

\section{Neglected Effects}\label{sec:neglected}
Since one goal of this paper was to obtain a detailed understanding of atmospheric evolution with a simple model, we have necessarily ignored   effects of potential significance.  We briefly address the most important of these and note that a followup work, Piso, Youdin \& Murray-Clay (in prep., hereafter Paper II), will extend our current models to address some of these effects.

>>>>

Many static studies reproduce a canonical $\MC \sim 10 M_\oplus$.  However, \citet[hereafter R06]{rafikov11, rafikov06} finds a wide range of values, $0.1 M_\oplus \lesssim \MC \lesssim 100 M_\oplus$, depending on the planetesimal accretion rate and disk parameters. % \citep[see also][]{Raf11}.  
Section \ref{sec:placc} compares our results to R06.  A general limitation of static models is the neglect of heat generated by atmospheric collapse, which can transform the core accretion instability into a slower process of Kelvin-Helmholtz (KH) contraction.

@@

This paper is organized as follows. Section \S\ref{sec:model} describes our model of atmospheric growth.  In Section \S\ref{sec:coolingan}, we develop a simplified analytic version of our atmospheric model.  We describe the structure and evolution of our atmosphere solutions in Section \S\ref{sec:KH}.   Section \S\ref{sec:critical} gives our final results for growth timescales and critical core masses.  We discuss some neglected effects in Section \S\ref{sec:neglected1} and summarize our findings in Section \S\ref{sec:conclusions}.  Some detailed derivations are presented in the appendices.

@@

To model the accretion of gas by a solid protoplanet, we develop a simplified two-layer model for time-dependent atmospheric growth via cooling, i.e. KH contraction.  With a convective interior and radiative exterior, this model is motivated by similar models of hot Jupiters \citep{arras06, youdin10}.

@@

\section{Neglected Effects}\label{sec:neglected1}
Since one goal of this paper was to obtain a detailed understanding of atmospheric evolution with a simple model, we have necessarily ignored   effects of potential significance.  We briefly address the most important of these and note that a followup work, Piso, Youdin \& Murray-Clay (in prep., hereafter Paper II), will extend our current models to address some of these effects.
